%-------------------------
% Resume in Latex
% Author : Joshua Wyllie
% Based on: Sourabh Bajaj repo
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

% Page coloring, fonts, and logos
\usepackage{pagecolor}
\usepackage{lato}
\renewcommand{\familydefault}{\sfdefault}
\usepackage{fontawesome}
% ---

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
% ---

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
% ---

% Custom commands
\newcommand{\resumeItem}[1]{%2
  \item\small{
    %\textbf{#1}
    #1
    %{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{8pt}\item%-1
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubSubheading}[2]{
    \vspace{1pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeTech}[2]{
 \textbf{#1:} #2
}

% COLOR THEMES SELECTION
% For Light theme un-comment this and comment the Dark theme section below
\colorlet{urlcolor}{blue}
\newcommand{\otherThemeRef}{\href{https://github.com/j-wyllie/resume/raw/master/joshua_wyllie_dark.pdf}{Get dark theme}}
\newcommand{\latestVersion}{\href{https://github.com/j-wyllie/resume/raw/master/joshua_wyllie_light.pdf}{Get latest version \faicon{refresh}}}

% For Dark theme un-comment this and comment the Light theme section above

%\colorlet{textcolor}{white!80!gray}
%\colorlet{backgroundcolor}{black!30!gray}
%\colorlet{urlcolor}{blue!25!white}
%\AtBeginDocument{\color{textcolor}}
%\newcommand{\otherThemeRef}{\href{https://github.com/jwyllie/resume/raw/master/joshua_wyllie_light.pdf}{Get light theme}}
%\newcommand{\latestVersion}{\href{https://github.com/jwyllie/resume/raw/master/joshua_wyllie_dark.pdf}{Get latest version \faicon{refresh}}}
% ---

% DOCUMENT MAIN
\begin{document}

% For Dark theme also un-comment this line:
%\pagecolor{backgroundcolor}

% HEADING
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://linktr.ee/wilmerags}{\Large Joshua Wyllie}} &  \href{https://github.com/j-wyllie}{ \faicon{github} \color{urlcolor} j-wyllie} \\
  \href{mailto:joshuawyllie@live.com}{joshuawyllie@live.com} &  \faicon{code} Python, R\\
    \href{mailto:joshuawyllie@live.com}{022 137 9514} & \textsl{\small \otherThemeRef} \\
  \textsl{\small \latestVersion} 
\end{tabular*}
% ---

% EXPERIENCE
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Solnet}{Wellington, New Zealand}
      {Junior Software Engineer}{September 2019 - Present}
      \resumeItemListStart
      \resumeItem{
      Designed and develop workflows for topic modeling and community detection to analyze hundred-thousand-scale text and network data.}
      \resumeItem{Sped up the analytical workflow by 75\% by redesigning the sampling strategy for jobs.}
      \resumeItem{Generated CLI tool for automation of predefined analysis workflows.}
\resumeItemListEnd
\resumeTech{Technologies}{Python, R, Bash, Gephi and Power BI.}\\
\resumeTech{Theory}{Topic modeling, Community detection, Network Analysis and NLP.}

\resumeSubheading
      {NoNoRank}{Uppsala, Sweden}
      {Machine learning engineer}{February 2019 - August 2019}
      \resumeItemListStart
      \resumeItem{Implemented Deep learning model for classifying malicious urls using only urls' text features, achieving 90\% of baseline accuracy by adapting state-of-the-art models on urls classifications.}
      \resumeItemListEnd
      \resumeTech{Technologies}{Python, Elasticsearch and Spark.}\\
      \resumeTech{Theory}{Deep learning and Text classification.}


% \newpage

\resumeSubHeadingListEnd
% ---

% EDUCATION
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Uppsala University}{Uppsala, Sweden}
      {Exchange Program B.Sc in Computer Science}{Sept. 2012 -- Jun. 2018}
      \resumeItemListStart
      \resumeItem{Took elective courses on: Introduction to data science, Advanced topics in data science, Artificial Intelligence, Data mining, Text mining, NoSQL databases, Digital image processing.}
      \resumeItem{(Thesis title) AdaBnn: Binarized Neural Networks trained with adaptive structural learning.}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Canterbury}{Christchurch, New Zealand}
      {B.Sc in Computer Science}{Sept. 2012 -- Jun. 2018}
      \resumeItemListStart
      \resumeItem{Took elective courses on: Introduction to data science, Advanced topics in data science, Artificial Intelligence, Data mining, Text mining, NoSQL databases, Digital image processing.}
      \resumeItem{(Thesis title) AdaBnn: Binarized Neural Networks trained with adaptive structural learning.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
% ---

\hfill \textsl{ \faicon{link}Following sections items are clickable for references.}

% CERTIFICATIONS
\section{Certifications}
  \resumeSubHeadingListStart
      \resumeSubheading
      {Amazon Web Services}{MOOC}
     {\href{https://www.coursera.org/account/accomplishments/records/J76SQGG4PVYL}{AWS Certified Developer Associate}}{Issued August 2020}
  \resumeSubHeadingListEnd
  
  \resumeSubHeadingListStart
    \resumeSubheading
      {Coursera}{MOOC}
      {\href{https://www.coursera.org/account/accomplishments/verify/BHN34W5WKBUT}{Structuring Machine Learning Projects}}{Issued May 2020}
      
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/records/J76SQGG4PVYL}{Improving Deep Neural Networks: Hyperparameter tuning, Regularization and Optimization}}{Issued May 2020}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/verify/MBWJ69CVLQAZ}{Neural Networks and Deep Learning}}{Issued May 2020}
     
    \resumeSubSubheading
     {\href{https://www.coursera.org/account/accomplishments/certificate/WYGG7TDFPB3F}{Data Visualization}}{Issued March 2016}
  \resumeSubHeadingListEnd
% ---

% PROJECTS
\section{Projects}

  \resumeSubHeadingListStart
    \resumeSubItem{\href{https://github.com/wilmeragsgh/adabnn}{AdaBnn: Binarized Neural Networks trained with adaptive structural learning.}}

    \resumeSubItem{\href{https://github.com/wilmeragsgh/WarmChat}{WarmChat: This app is a small chat room that classify every message and say weather is an insult or not using four classifiers: svm, random forest, decision trees and max entropy.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/term_freq_linkedin}{Small tool for generating frequent words analysis on the position names of LinkedIn Connections.}}
    
    \resumeSubItem{\href{https://github.com/wilmeragsgh/shinycker}{Template for Dockerized Shiny (R) application deployment.}}
    
  \resumeSubHeadingListEnd
% ---


\hfill \textsl{ Not clickable anymore.}
% PROGRAMMING SKILLS
\section{Other programming tools}
  \resumeSubHeadingListStart
  \resumeSubItem{\textbf{Cloud services:} AWS(Lambda, S3, Sagemaker), Azure(Blob storage).}
  
  \resumeSubItem{\textbf{Deep learning frameworks:} Keras, Tensorflow.}
  
  \resumeSubItem{\textbf{R:} dplyr, ggplot, tidyr, shiny, plumber.}
  
  \resumeSubItem{\textbf{Python:} xgboost, sci-kit, pandas, falcon, flask.}
  
  \resumeSubItem{\textbf{Webserver:} Gunicorn.}
  
  \resumeSubHeadingListEnd

% ---
\end{document}
